Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code

### 2019-01-23 paper/ICPC19/icpc19.tex
update paper + cleaning

\begin{abstract}
  Security is a crucial non-functionality requirement for software applications.
  However, building secure software is far from trivial as developers lack both
  the knowledge and tools to effectively address this concern. In this paper, we
  study the impact of changes to improve security on the maintainability of several
  open source applications. Using a dataset containing 643 security-oriented
  commits, we measure maintainability --- as computed by the Software Improvement
  Group's web-based source code analysis service \emph{Better Code Hub} (BCH) ---
  before and after the security refactoring. Results show that making software
  more secure comes at a cost on maintainability. This is particularly evident
  in refactorings to deal with Broken Authentication and Cross-Site Request Forgery attacks.
  Furthermore, we have found evidence that security-related changes are more
  likely to be modified in the future than regular code changes.
\end{abstract}

@@

@@

\section{Conclusion}

@@

>>>>

\begin{abstract}
  Security is a crucial non-functionality requirement for software applications.
  However, building secure software is far from trivial as developers lack both
  the knowledge and tools to effectively address this concern. In this paper, we
  study the impact of changes to improve security on the maintainability of several
  open source applications. Using a dataset containing 643 security-oriented
  commits, we measure maintainability --- as computed by the Software Improvement
  Group's web-based source code analysis service \emph{Better Code Hub} (BCH) ---
  before and after the security refactoring. Results show that making software
  more secure comes at a cost on maintainability. This is particularly evident
  in refactorings to deal with \textit{Broken Authentication} and \textit{Cross-Site Request Forgery} attacks.
  Furthermore, we have found evidence that security-related changes are more
  likely to be modified in the future than regular code changes.
\end{abstract}

@@

\section{Motivation and Research Questions}

\textcolor{mypink3}{Ver que exemplos existem na amostra da secbench que vamos utilizar para dar como exemplo de motivacao}

@@

\section{Conclusion and Future Work}

@@

Better Code Hub?
